
\section{\mysidestyle Awards} 

    \href{https://www.ybca.org/ybca-fellows}
  {\textbf{YBCA Fellow}}
   \textsl{Yerba Buena Center for the Arts} 
    \hfill \textsl{May 2018} \\
    {\small YBCA fellows are accepted through a competitive application and meet throughout the year to create public works of art addressing critical social themes. My work focuses on creating citizen accountability and responsibility for collective safety, policing, and the rule of law.}
    
  {\textbf{SCPD Teaching Award}}
   \textsl{Stanford Center for Professional Development} 
    \hfill \textsl{Jan. 2018} \\
    {\small I received this award in recognition of my work supporting distance learning students in my design and teaching of BIOMEDIN 215: Data-Driven Medicine.}    

    \href{https://vpge.stanford.edu/fellowships-funding/dare}
  {\textbf{DARE Fellow}}
   \textsl{Stanford Vice Provost of Graduate Education} 
    \hfill \textsl{Aug. 2017} \\ 
    {\small DARE (Diversifying Academia, Recruiting Excellence) is a competitive and prestigious two-year full fellowship and training program for Stanford graduate students working to create an equitable and just academic culture.}

 \textbf{Research Project Grant (R01)}
   \textsl{NIH} 
    \hfill \textsl{Funded July 2017} \\ 
    {\small I conceived of the outline for this multi-million dollar grant awarded to the Shah lab and collaborators. I also wrote the entirety of the third aim, which addresses machine learning methods for causal inference using electronic health records data.}

 \textbf{Learning Guidelines}
   \textsl{AstraZeneca and Stanford Center for Clinical Research} 
    \hfill \textsl{Funded July 2016} \\ 
    {\small I wrote the entirety of this quarter-million dollar grant awarded to the Shah Lab. I proposed learning treatment guidelines by applying heterogenous treatment effect models to electronic health records data. I write quarterly updates to keep funders abreast of our progress.}

	\href{https://biosciences.stanford.edu/current/diversity/advance/}
	{\textbf{ADVANCE Institute Fellow}}
   \textsl{Stanford Biosciences Office of Graduate Education} 
    \hfill \textsl{June 2014} \\ 
 {\small ADVANCE fellows receive professional development training to promote success in graduate school.}