
\section{\mysidestyle Teaching}

	\href{https://drive.google.com/file/d/1ot75uaaug10OrRX6AOHW08pIJS6d0eam/view?usp=sharing}
	{\textbf{Course Designer}}
	\textsl{BIOMEDIN 215: Data-Driven Medicine}
	\hfill \textsl{June 2016 to Jan. 2018} \\ 
    {\small I created a course that teaches MS-level students in technical fields how to execute and evaluate studies in clinical informatics. I created learning goals and designed each lecture to accomplish subgoals. I designed homework to provide practice in programming and statistics skills, and introduced journal club presentations to cultivate critical reading skills. I incorporated active learning techniques and fostered an inclusive environment throughout the course. I was supported by a competitive grant through Stanford's office of the Vice Provost for Graduate Education.} 

        	\textbf{Lecturer}  
	\textsl{BIOMEDIN 215: Data-Driven Medicine}
	\hfill \textsl{Fall 2016, 2017} \\ 
        {\small I delivered about half of the lectures in the course, focusing on those with statistical or machine learning content} 
        
        \textbf{Teaching Assistant} 
	\textsl{BIOMEDIN 215: Data-Driven Medicine}
        \hfill \textsl{Fall 2016, 2017} 
%        {\small As TA, I evaluated the effectiveness of each lecture vis-a-vis the learning goals, mentored students in office hours, and provided logistical support to the course.}

	\href{https://vptl.stanford.edu/students/graduate-students/ta-handbook/liaisons-consultants-and-mint-programs}
	{\textbf{Program Liason}}
        \textsl{Vice Provost for Teaching and Learning} 
 	\hfill \textsl{Sept. 2016 to present} \\ 
    {\small I foster two-way communication between the VP for Teaching and Learning and the Biomedical Informatics training program by promoting programs and resources and customizing teaching services.}
    
     \href{https://vptl.stanford.edu/faculty-staff-student-instructors/diversity-inclusion/resources/teaching-toolkits/identity-classroom}
     {\textbf{Inclusive Teaching Workgroup Member}}
     \textsl{Vice Provost for Teaching and Learning} 
     \hfill \textsl{Spring 2017} \\ 
    {\small Research shows that good teaching is inclusive teaching. The working group collaborated to share research, resources, and personal experience relating to best practices for inclusive teaching. We created teaching guides for the VP for Teaching and Learning website and future workshops.}
    
     \textbf{Teaching Assistant} 
     \textsl{BIOMEDIN 210: Modeling Biomedical Systems} 
     \hfill \textsl{Winter 2016} \\ 
    {\small I redesigned several homework assignments to better reflect the learning goals, delivered a chalkboard lecture on probabilistic graphical models, held office hours, mentored student project groups, and provided logistical support.}
    
    \href{https://statistics.stanford.edu/resources/consulting}
    {\textbf{Consultant}}
    \textsl{Stanford Statistical Consulting Services} 
    \hfill \textsl{Fall 2016} \\ 
    {\small I provided consultations to over 25 Stanford researchers using statistical methods in their work. Clients came with a great diversity of backgrounds and with problems of varying complexity. I interviewed each client to understand their goal and their data before discussing potential solutions. I taught my client the statistical ideas that justified each proposal, avoiding jargon and tailoring the explanations to their statistical experience. My clients reported high satisfaction with my solutions and often later remarked that the ideas I taught them became valuable in other projects or had helped them redefine the research question they were asking.}